%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \documentclass[]{deedy-resume-openfont}
  
      \begin{document}
      
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %
  %     Profile
  %
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  
\namesection{Harinder} {Singh}\infoline{\href{mailto:harindersingh2107@gmail.com}{harindersingh2107@gmail.com} | 8901116612 | Sirsa,Haryana}\\\vspace{4pt}\linksline{\descript{\href{https://www.linkedin.com/in/harindersingh441/}{Linkedin | }}\descript{\href{https://github.com/Harinder441}{GitHub | }}\descript{\href{https://www.crio.do/learn/portfolio/harindersingh2107}{Portfolio}}}\underlineheader{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\raggedright

    \runsubsection{Crio.Do}\hspace*{\fill}  \location{May 2023 - March 2024}\\
    \descript{Fellowship Program -Software Development}\hspace*{\fill}\location{Remote}\\
    
    \sectionsep
  

    \runsubsection{Akal University}\hspace*{\fill}  \location{July 2019 - Dec 2022}\\
    \descript{Bachelors Mathematics}\hspace*{\fill}\location{Talwandi Sabho, Punjabb}\\
    CGPA: 9.0\\
    \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %
        %     Experience
        %
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \section{Experience}
        \runsubsection{Kalgidhar Trust,}\descript{| Full Stack Web Developer}\hfill \location{Remote (Delhi/India) | Jun 2023 – Present}
            \vspace{4pt}
\begin{tightemize}
\item Utilizing React, Inertia, Laravel 9, and MySQL for project development.
\item Designed and implemented a visually appealing admin panel for student examination, Bug Tracker, Student Portal and expense management using Material UI React.
\item Developed robust and user-friendly features to enhance overall application functionality.
\item Successfully managed project timelines and delivered projects on time.
\end{tightemize}
            \sectionsep
        \runsubsection{Business Web Solutions}\descript{| Web Developer}\hfill \location{Remote | Mar 2023 – May 2023}
            \vspace{4pt}
\begin{tightemize}
\item Developed websites using React js.
\item Implemented responsive design and user-friendly interfaces to enhance the user experience.
\item Collaborated with a team to ensure seamless integration of front-end and back-end components for a dynamic and interactive web application.
\item  \custombold{Skills} - HTML/CSS \textbar{}Javascript \textbar{}React js.\textbar{}Web Development.
\end{tightemize}
            \sectionsep
        \runsubsection{IIT Dhanbad}\descript{| Research Intern}\hfill \location{Dhanbad,Jharkhand | July 2022 – Aug 2022}
            \vspace{4pt}
\begin{tightemize}
\item Implemented portfolio optimization models using SVM and fuzzy SVM.
\item Conducted independent research and development during the internship, resulting in improved portfolio performance.
\item  \custombold{Skills } - Python \textbar{} Machine Learning \textbar{} Optimization
\end{tightemize}
            \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\raggedright
\begin{longtable}{p{5cm}p{13.5cm}}
\descript{Programming Languages} & {\location{Javascript, Pytrhon, HTML, CSS, C, C++, PHP}} \\
\descript{Libraries/Frameworks} & {\location{React js, Inertia js, PHP Laravel, Flask, Bootstrap 5, Tkinter, Node js}} \\
\descript{Tools / Platforms} & {\location{Github, Notion}} \\
\descript{Databases} & {\location{MySQL, MongoDB}} \\
\end{longtable}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %
        %     Projects
        %
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \section{Projects / Open-Source}
        \vspace{2mm}
        \raggedright
        
            \runsubsection{\large{QKart}}
            \descript{| \href{https://qkart-backend-harinder.onrender.com/}{Link}}\hfill \location{Javascript,React Js, Node Js, MongoDB, Mongoose, Jest,}\\
            \begin{tightemize}
\item[] QKart is an E-commerce application offering a variety of products for customers to choose from.
\item[] During the course of this project,
\item  Implemented the core logic for authentication, shopping cart and checkout
\item  Improved UI by adding responsive design elements for uniform experience across different devices
\item  Built the complete set of REST APIs for an E-commerce application following the best practices
\item  Used MongoDB NoSQL database for data storage
\item  Wrote unit and integration tests to test the implementation
\end{tightemize}
            \sectionsep
          
        
            \runsubsection{\large{My Portfolio Website}}
            \descript{| \href{http://harindersinghportfolio.onrender.com/}{Link}}\hfill \location{HTML/CSS, Javascript, Python, Flask, jinja2, Git, Bootsrap 5, SQL}\\
            \begin{tightemize}
\item Developed and deployed a portfolio website using Flask, Python and Git, fully responsive and dynamic.
\item Implemented an authentication method to allow for editing and updating of website content.
\item Got experience in deploying web applications using Git, Render.com and ElephantSQL
\end{tightemize}
            \sectionsep
          
        
            \runsubsection{\large{Stack overflow clone}}
            \descript{| \href{https://github.com/Harinder441/stack-overflow-clone-mern}{Link}}\hfill \location{HTML /CSS, Bootstrap, Javascript, React Js}\\
            \begin{tightemize}
\item A Frontend Stack Overflow clone built using the React js featuring dashboard for user login/signup, options to add new questions, voting system, and other features.
\end{tightemize}
            \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Awards
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Honors \& Awards}
\vspace{4pt}
\begin{tightemize}
\item Got certification for C, C++ and Python Programming Language from Bombay IIT\\
\item Secured 1st Rank in Programming war, Technophilia 2022, Akal University\\
\item Solved 57\% DSA Problems using C language at coder.MysirG.com\\
\end{tightemize}
      \ 
      \end{document}